Ce que j'ai compris jusqu'à maintenant\\Début de rapport ?

### 2025-04-02 article_bihom_v2.tex
c'est finalement semi-régulier

		However, after some tests and after applying F5-matrix algorithm on polynomial systems generated by NSBC instances, we get reductions to 0, this means that the polynomial systems are not semi-regular.

		\subsection{Bilinear systems case}
		Our NSBC instances are quadratic systems that are bilinear in the variables of degree 2, are not semi-regular and overdetermined.

		We will note $n_x$ (resp. $n_y$) the number of variables in $x$ (resp. number of variables in y). In our case, $n_x = n_y = (m-1)/2$ and $m = k$. As we mentioned earlier, our polynomials systems are not-semi regular, so we get reductions to 0 during the F5 algorithm using the Frobenius criterion for boolean polynomial systems.

@@

		 No need to say that it's useless to use the criterion as shown in \cite{FSS11} without adapting it to get an advantage.
		 This can be explained by the fact that the extended criterion computes reduced polynomials of degree $n_x$ and $n_y$ and in our case, $n_x$ and $n_y$ can be too big to compute. Maybe there could be a way to compute reduced polynomials of only degree 2 for our use case if we stop Macaulay matrix computations at degree 4 with our quadratic systems.
		 \newline
		 Note pour moi-même, il faut maintenant essayer de réaliser une implémentation de ce critère en sage ou avec hpXbred et BeanPolE pour voir comment ça se comporterait avec des petits systèmes et voir quel serait l'avantage ou le désavantage sachant que la supposition que toutes les lignes se réduisent à 0 est extrêment peu probable.

>>>>

		However, after some tests and after applying F5-matrix algorithm on polynomial systems generated by NSBC instances, we get reductions to 0, this means that the polynomial systems are not semi-regular when we only multiply by the $x$ variables or by the $y$ variables. If we multiply by the $x$ variables and at least one $y$ variable, we get no reductions to 0 i.e. the system is semi-regular

		\subsection{Bilinear systems case}
		Our NSBC instances are quadratic systems that are bilinear in the variables of degree 2, overdetermined and can be semi-regular.

		We will note $n_x$ (resp. $n_y$) the number of variables in $x$ (resp. number of variables in y). In our case, $n_x = n_y = (m-1)/2$ and $m = k$. As we mentioned earlier, our polynomials systems can be semi-regular, so we get no reductions to 0 during the F5 algorithm using the Frobenius criterion for boolean polynomial systems.

@@

		 No need to say that it's useless to use the criterion as shown in \cite{FSS11} without adapting it to get an advantage.
		 This can be explained by the fact that the extended criterion computes reduced polynomials of degree $n_x$ and $n_y$ and in our case, $n_x$ and $n_y$ can be too big to compute. Maybe there could be a way to compute reduced polynomials of only degree 2 for our use case if we stop Macaulay matrix computations at degree 4 with our quadratic systems.

		 As the authors of \cite{FSS11} noted at the end of their article, generic bilinear systems are regular. They didn't show that for overdetermined systems but we saw that experimentally but it's yet to be proven.
		 \newline
		 Note pour moi-même, il faut maintenant essayer de réaliser une implémentation de ce critère en sage ou avec hpXbred et BeanPolE pour voir comment ça se comporterait avec des petits systèmes et voir quel serait l'avantage ou le désavantage sachant que la supposition que toutes les lignes se réduisent à 0 est extrêment peu probable.
